Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
order todos

\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$. By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{prop}
\label{prop:sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably
rooted  log stacky curves $R \subset R'$ be the corresponding
inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3,x_4
,x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
3}P$.

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec 
		y_4 \prec y_5$ and equip the ring $k[y_3,y_4,y_5,x]$ with the block 
		order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

>>>>

\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{prop}
\label{prop:sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably
rooted  log stacky curves $R \subset R'$ be the corresponding
inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3, x_4
, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
3}P$.

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec 
		y_4 \prec y_5$ 
		\todo{This order isn't quite right, we need $y_4^2 < y_5y_3$.}
		and equip the ring $k[y_3,y_4,y_5,x]$ with the block 
		order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}
